Market simulator

### 2020-11-13 analysis/05_market_simulator.Rmd
Got a button to work finally

# Organization configuration
organization_data <- reactive({
  if (is.null(input$org_update$datapath)) {
    organization_data <- org_default
  } else {
    eventReactive()
    req(input$org_update)
    organization_data <- read_csv(input$org_update$datapath)
  }
})

# organization_data <- reactive({
#   if (is.null(input$org_update$datapath)) {
#     organization_data <- org_default
#   } else {
#     req(input$org_update)
#     eventReactive(input$org_button, {
#       organization_data <- read_csv(input$org_update$datapath)
#     })
#   }
# })

# observeEvent(input$org_button, {
#   req(input$org_update)
#   organization_data$data <- read_csv(input$org_update$datapath)
# })

@@

```{r import}
# Organization file input
fileInput(
  "org_update",
  "Import Organization Data",
  accept = c(
    "text/csv",
    "text/comma-separated-values,text/plain",
    ".csv"
  )
)

actionButton(
  "org_button",
  label = "Update Organization Data"
)

@@

# Persona file input
fileInput(
  "per_update",
  "Import Persona Data",
  accept = c(
    "text/csv",
    "text/comma-separated-values,text/plain",
    ".csv"
  )
)

@@

# Render the persona configurations as a table
renderTable({
  req(input$per_update)

  per_import = read_csv(input$per_update$datapath)
  per_import
})
```

>>>>

# Organization configuration
# organization_data <- reactive({
#   if (is.null(input$org_update$datapath)) {
#     organization_data <- org_default
#   } else {
#     req(input$org_update)
#     organization_data <- read_csv(input$org_update$datapath)
#   }
# })

# organization_data <- reactive({
#   org_file_input <- input$org_update
#   if (is.null(org_file_input)) {
#     organization_data <- org_default
#   } else {
#     req(input$org_update)
#     eventReactive(input$org_button, {
#       organization_data <- read_csv(input$org_update$datapath)
#     })
#   }
# })
# 
# organization_data <- reactive({
#   organizaiton_data <- org_default
# })
# 
# eventReactive(input$org_button, {
#   req(input$org_update)
#   organization_data$data <- read_csv(input$org_update$datapath)
# })

@@

```{r import}
# let the user choose the type of input file
radioButtons(
  inputId = "what_config",
  label = "Choose Configuration",
  choices = c("Default", "User input"),
  selected = "Default",
  inline = FALSE
  )

# render file input widgets conditioned on user choice

# Organization file input
conditionalPanel(condition = 'input.what_config == "User input"',
                 fileInput(
                   "org_update",
                   "Import Organization Data",
                   accept = c(
                     "text/csv",
                     "text/comma-separated-values,text/plain",
                     ".csv"
                   )
                  ),
                 actionButton(
                   "org_button",
                   label = "Update Organization Data"
                  )
                 )

# Persona file input
conditionalPanel(condition = 'input.what_config == "User input"',               
                fileInput(
                  "per_update",
                  "Import Persona Data",
                  accept = c(
                    "text/csv",
                    "text/comma-separated-values,text/plain",
                    ".csv"
                  )
                ),
                actionButton(
                  "per_button",
                  label = "Update Persona Data"
                )
              )

 # observeEvent(input$org_button, {
 #   req(input$org_update)
 #    organization_data <- read_csv(input$org_update$datapath)
 #  })

# deal with the file selected by the user
organization_data <- reactive({
  if (input$what_config == "Default") {
    x <- org_default
  } else {
    if (input$what_config == "User input") {
      req(input$org_button)
      req(input$org_update)
      x <- read_csv(input$org_update$datapath)
    }
  }
})

# organization_data <- reactiveValues(data = NULL)

# deal with the file selected by the user
# organization_data <- reactive({
#   if (input$what_config == "Default") {
#     x <- org_default
#   }
# })
# 
# observeEvent(input$org_button, {
#   req(input$org_update)
#   organization_data$data <- read_csv(input$org_update$datapath)
# })

# deal with the file selected by the user
# organization_data <- reactive({
#   if (input$what_source == "Default") {
#     x <- org_default
#   }
# })

# fileInput(
#   "org_update",
#   "Import Organization Data",
#   accept = c(
#     "text/csv",
#     "text/comma-separated-values,text/plain",
#     ".csv"
#   )
# )

# actionButton(
#   "org_button",
#   label = "Update Organization Data"
# )

@@

# Persona file input
# fileInput(
#   "per_update",
#   "Import Persona Data",
#   accept = c(
#     "text/csv",
#     "text/comma-separated-values,text/plain",
#     ".csv"
#   )
# )

@@

# Render the persona configurations as a table
# renderTable({
#   req(input$per_update)
#   
#   per_import = read_csv(input$per_update$datapath)
#   per_import
# })
```
